---
title: "Quantitative Analysis"
output: html_document
---

Once again, we start by loading our key libraries
```{r}
library(readxl)
library(tidyverse)
library(scales)
library(RColorBrewer)

```

# 1 Exports of pork meat from Spain to China and the EU.

Here, we plan to create a bar chart that shows the evolution of pork emat exports from
Spain to China and the rest of EU countries. I gathered the data from the Spanish
Government and manually created an excel file. Let's read that excel file ;)

```{r}
exports<- read_excel("data/pigmeat_exports2.xlsx")
```

Now, we are dealing with large numbers. To turn of R's scientific notation in our map, we will
run the following command stating that are should only use it after a given limit.

```{r}
options(scipen=2000000000)
```

The only thing left to do it to plot the yearly exports, the next command takes care of it.

```{r}
ggplot(data = exports, mapping = aes(x=Year, y=Tonnes, fill=Destination)) +
  scale_fill_manual(values = c("bisque4", "black"))+
  geom_bar(stat="identity", position = "dodge")
```

And here is our bar chart showing the yearly export of pigmeat from Spain to
China and the EU

# 2 Imports of soy to Spain (global data)

Lastly, there one data source left to provide here is the trade matrix I used
to find out that almost two thirds of the soy imported to Spain comes from
Argentina. There is no need to manipulate the dataset, but I feel like it
is important to share it here as to add transparency to my project. I obtained
the data from FAOSTAT and manually calculated the percentages.


```{r}
imports<- read_csv("data/Imports_feed_Spain_2019.csv")
```

